---
output: github_document
title: "randomizr for Stata: Easy to use tools for common forms of random assignment and sampling"
---

**randomizr** is designed to make conducting field, lab, survey, or online experiments easier by automating the random assignment process. Social and lab scientists conducting experiments need a process to assign individuals or units of observation to treatment or control wings. Common designs include simple random assignment, complete randomization, block randomization, cluster randomization, and blocked cluster randomization. **randomizr** automates all of these processes and assists scientists in doing transparent, replicable science. 

## randomizr for Stata

Installing the latest stable version of **randomizr** from ssc is easy:

```{r eval=FALSE}
ssc install randomizr
```

If you would like to install the latest development release directly from GitHub, run the following code:

```{r eval=FALSE}
net install randomizr, from(https://raw.githubusercontent.com/DeclareDesign/strandomizr/master/) replace
```

## Getting started with randomizr for Stata

`complete_ra` (complete randomization) is the workhorse function that will be most appropriate for a large number of experimental situations: it assigns m of N units to treatment:

```{r eval=FALSE}
ssc install randomizr
set obs 100
complete_ra, m(50)
```

A Stata version of our [online tutorial](https://declaredesign.org/stata/randomizr/articles/strandomizr_vignette.html) is also available.

Happy randomizing!
